SAT Competition 2020\tnoteref{title}

### 2021-06-22 paper/main.tex
fixed overfull hboxes
more consistent table labeling

For the Planning track,
the benchmark instances were generated using two SAT-based planners
\emph{Madagascar}~\cite{Madagascar14} and \emph{Pasar}~\cite{Pasar19}. We used
Madagascar both in its default configuration to generate a parallel encoding
based on $\exists$-step plans and to generate a sequential encoding. Pasar uses
the \emph{grounding routine} deployed by the well-known planner \emph{Fast
  Downward}~\cite{FastDownward06} to translate planning tasks into a different
formalism and then encodes it to SAT using a parallel encoding.
% For planning tasks where this makespan cannot be determined with
% available computational resources, we use a \emph{sequential} encoding, where
% the minimal makespan equals the length of the shortest valid plan. Together with
% known bounds\footnote{Upper and lower bounds on plan length are available for
% 	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
% 	actions.} on the optimal plan length
%   we can generate satisfiable and unsatisfiable SAT formulas
%   for hard planning problems.
%\textcolor{red}{global note: should try to be consistent with present/past tense...}
The classical planning benchmarks were selected from the \emph{Satisfying} and
\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}. We
only selected planning domains with \emph{unit cost} and eliminated those that
% are designed to be challenging for the grounding routine and
take more than 100 GB of memory to encode into SAT. We ran both Pasar and
Madagascars $\exists$-configuration with a timeout of 3 hours on the
remaining instances to find the minimal makespans. For each planning task where
this process did not timeout, we generated a pair of satisfiable and
unsatisfiable SAT instances. A significant number of instances from this set were not used
as \solver{Minisat} could solve them in under $10$ minutes.
% From those we discarded the SAT formulas that \solver{Minisat} can solve in
% under $10$ minutes.
We augmented the remaining domains with the last unsatisfiable formulas
generated for planning task where the minimal makespan could not be found.
To generate the missing benchmarks we use a \emph{sequential} encoding
% , where the minimal makespan equals the length of the shortest valid plan
together with known bounds\footnote{Upper and lower bounds on plan length are available for
	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
	actions.} on the optimal plan length.

In addition to the classical planning problems, we also included SAT instances
generated by \emph{Tree-REX} \cite{TreeRex19}, a planner for \emph{Hierarchical
	Task-networks} (HTN). In HTN planning the planner is provided with additional domain
knowledge besides the problem description. The HTN benchmarks were provided by
the solver author.

@@

\begin{table}[t]
	\centering\small
	\begin{tabular}{llrr}
		\multicolumn{2}{l}{Encoding} & SAT                       & UNSAT       \\
		\hline\arrayrulecolor{lightgray}
		\textbf{H}                   & Tree-REX                  & 15    & 11  \\
		\textbf{P}                   & Pasar                     & 14    & 14  \\
		\textbf{ME}                  & Madagascar $\exists$-step & 5     & 10  \\
		\textbf{MS}                  & Madagascar sequential     & 66    & 65  \\
		\hline
		                             &                           & 100   & 100 \\
	\end{tabular}
	\label{tab:planningBenchmarkDist}
	\caption{Number of planning instances generated per encoding.}
\end{table}

@@

\paragraph{Quantified Boolean Formulas (QBF)}
\textsf{Ijtihad} is a QBF solver which uses counterexample-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}

@@

Turning to the Parallel track, Figure~\ref{fig:res-parallel} shows the performance of
all participating parallel solvers. 
The best solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. Interestingly,
this solver used 32 threads on the 64 virtual cores that were available. In fact, it has been observed in already 
recent earlier 
SAT competitions that using fewer threads than the number of available virtual cores can be helpful; as threads compete 
for memory, using all virtual cores may be detrimental to  overall performance. The runner up is \solver{Plingeling}, while the
third place goes to \solver{ManyGlucose-32}. 
Interestingly, one can observe from Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR*} solvers
and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
It appears still to be challenging to beat the best-performing sequential solvers with
with a parallel solver. (In fact, as we will show later on, sequential portfolios including only a few
Main track solvers show  better performance than all of the parallel solvers.)

>>>>

For the Planning track,
the benchmark instances were generated using two SAT-based planners
\emph{Madagascar}~\cite{Madagascar14} and \emph{Pasar}~\cite{Pasar19}. We used
Madagascar both in its default configuration to generate a parallel encoding
based on $\exists$-step plans and to generate a sequential encoding. Pasar uses
the \emph{grounding routine} deployed by the well-known planner \emph{Fast
  Downward}~\cite{FastDownward06} to translate planning tasks into a different
formalism and then encodes it to SAT using a parallel encoding.
% For planning tasks where this makespan cannot be determined with
% available computational resources, we use a \emph{sequential} encoding, where
% the minimal makespan equals the length of the shortest valid plan. Together with
% known bounds\footnote{Upper and lower bounds on plan length are available for
% 	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
% 	actions.} on the optimal plan length
%   we can generate satisfiable and unsatisfiable SAT formulas
%   for hard planning problems.
%\textcolor{red}{global note: should try to be consistent with present/past tense...}
The classical planning benchmarks were selected from the \emph{Satisfying} and
\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}. We
only selected planning domains with \emph{unit cost} and eliminated those that
% are designed to be challenging for the grounding routine and
take more than 100 GB of memory to encode into SAT. We ran both Pasar and
Madagascars $\exists$-configuration with a timeout of 3 hours on the
remaining instances to find the minimal makespans. For each planning task where
this process did not timeout, we generated a pair of satisfiable and
unsatisfiable SAT instances. A significant number of instances from this set were not used
as \solver{Minisat} could solve them in under $10$ minutes.
% From those we discarded the SAT formulas that \solver{Minisat} can solve in
% under $10$ minutes.
We augmented the remaining domains with the last unsatisfiable formulas
generated for planning task where the minimal makespan could not be found.
To generate the missing benchmarks we use a \emph{sequential} encoding
% , where the minimal makespan equals the length of the shortest valid plan
together with bounds\footnote{Upper and lower bounds on plan length are available for
	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
	actions.} on the optimal plan length.

In addition to the classical planning problems, we also included SAT instances
generated by \emph{Tree-REX} \cite{TreeRex19}, a planner for \emph{Hierarchical
	Task-networks} (HTN).
  In HTN planning additional domain knowledge besides the problem description is provided.
The HTN benchmarks were provided by
the solver author.

@@

\begin{table}[t]
	\centering\small
	\begin{tabular}{llrr}
		\multicolumn{2}{l}{Encoding} & SAT                       & UNSAT       \\
		\hline\arrayrulecolor{lightgray}
		\textbf{H}                   & Tree-REX                  & 15    & 11  \\
		\textbf{P}                   & Pasar                     & 14    & 14  \\
		\textbf{ME}                  & Madagascar $\exists$-step & 5     & 10  \\
		\textbf{MS}                  & Madagascar sequential     & 66    & 65  \\
		\hline
		 $\Sigma$                    &                           & 100   & 100 \\
	\end{tabular}
	\label{tab:planningBenchmarkDist}
	\caption{Number of planning instances generated per encoding.}
\end{table}

@@

\paragraph{Quantified Boolean Formulas}
\textsf{Ijtihad} is a QBF solver which uses counterexample-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}

@@

Turning to the Parallel track, Figure~\ref{fig:res-parallel} shows the performance of
all participating parallel solvers. 
The best solver here is \solver{Painless-MCOMSPS-STR32}. Interestingly,
this solver used 32 threads on the 64 virtual cores that were available. In fact, it has been observed in already 
recent earlier 
SAT competitions that using fewer threads than the number of available virtual cores can be helpful; as threads compete 
for memory, using all virtual cores may be detrimental to  overall performance. The runner up is \solver{Plingeling}, while the
third place goes to \solver{ManyGlucose-32}. 
Interestingly, one can observe from Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR*} solvers
and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
It appears still to be challenging to beat the best-performing sequential solvers with
with a parallel solver. (In fact, as we will show later on, sequential portfolios including only a few
Main track solvers show  better performance than all of the parallel solvers.)
